---
title: "Week 12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(PPBDS.data)
library(rstanarm)
library(tidyverse)

# Same data clean up as last week.

week_12 <- shaming %>% 
  mutate(age = 2006 - birth_year) %>% 
  mutate(treatment = fct_relevel(treatment, "Control")) %>% 
  mutate(solo = ifelse(hh_size == 1, TRUE, FALSE)) %>% 
  select(-general_04, -no_of_names, -birth_year, -hh_size) 
```


## Scene 1

**Prompt:** Create a fitted model object called `fit_1` using this formula or, if you want, a formula which you prefer. You are trying to model `age` as a function of various parameters.

age ~ sex + solo + primary_02 + primary_04 + treatment + sex:solo

```{r sc1}
fit_1 <- stan_glm(formula = age ~ sex + solo + primary_02 + primary_04 + treatment + sex:solo,
                  data = week_12,
                  refresh = 0, 
                  seed = 9)

```

                    
* Is this a causal or predictive model? Why?

Predictive - age is dependent

* Interpret the fitted model. 

Intercept - women who live alone, were not shamed, and did not vote in the past
2 primaries (age = 46.2072)

soloTRUE - 7.5 years older than women who didn't live alone
sexMale - 1.2 years older
sexMale:soloTRUE - 2.2 years younger

* Should we keep all these variables? And the interaction term?



* Are you surprised about the meaningfulness, or lack thereof, for the treatment variables?




## Scene 2

**Prompt:** Provide a posterior probability distribution for the expected difference in ages between those who live alone and those who do not. (Hint: Given that we are asking for an expected value, use `posterior_epred()`.)

```{r}
solo_t <- tibble(solo = c(FALSE, TRUE), primary_04 = "Yes", sex = "Male", primary_02 = "Yes")

fit_2 <- stan_glm(age ~ sex + solo + primary_02 + primary_04 + sex:solo,
                  data = week_12,
                  refresh = 0)

posterior_epred(fit_2, newdata = solo_t) %>%
  as_tibble() %>%
  rename(group = `1`, alone = `2`) %>%
  pivot_longer(values_to = "age", names_to = "solo", cols = group:alone) %>%
  ggplot(aes(x = age, fill = solo)) + 
    geom_histogram(bins = 100, alpha = 0.6, aes(y = after_stat(count/sum(count)))) + 
  theme_bw() + 
  labs(y = "Frequency",
       x = "Age",
       title = "Posterior Probability Distribution of Age as Function of Whether An Individual Lives Alone",
       subtitle = "For Men who Voted in the 2002 and 2004 Primary Elections")

```






